---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-", eval = TRUE,
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```

# snapsite

[![Travis-CI Build Status](https://travis-ci.org/leonawicz/snapsite.svg?branch=master)](https://travis-ci.org/leonawicz/snapsite)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/leonawicz/snapsite?branch=master&svg=true)](https://ci.appveyor.com/project/leonawicz/snapsite)
[![Coverage Status](https://img.shields.io/codecov/c/github/leonawicz/snapsite/master.svg)](https://codecov.io/github/leonawicz/snapsite?branch=master)

`snapsite` contains a collection of utility functions for the development, maintenance and refinement of `pkgdown`-derived documentation across multiple SNAPverse packages. The core of the documentation for a SNAPverse package is based around pkgdown, which builds documentation
for each package individually. The `snapsite` package assists with thematic tweaks and cohesive, standardized integration across
multiple packages in the verse, helping to bring the SNAPverse together. It is not relevant to the SNAPverse outside of this development context.
`snapsite` is a satellite package in the verse with `snapmeta` being the only SNAPverse package it is dependent on. It is not required by any other packages.

## Installation

You can install snapsite from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("leonawicz/snapsite")
```

## Usage

This package is in early development. Examples are limited. At the moment it includes a function for generating a basic flowchart of the SNAPverse.


```{r simple_verse_chart, echo = FALSE, results = "hide"}
library(snapsite) # image may require creation outside of this chunk, commented out line below
if(!file.exists("man/figures")) dir.create("man/figures")
#verse_diagram(file_name = "man/figures/README-simple_verse_chart-1.svg", title = "Simplified overview of the SNAPverse")
```

```{r simple_verse_chart_echo, eval = FALSE}
library(snapsite)
verse_diagram(title = "Simplified overview of the SNAPverse")
```

<p style="text-align:center;"><img src="man/figures/README-simple_verse_chart-1.svg"></p>

